Note on coherent state

### 2020-03-19 notes/coherent state.tex
主要写了一些关于Heisenberg-Weyl group的内容

    \section{Basic knowledges on oscillators}
        In this section, I'd like to briefly review some basic properties of some operators. The Hamiltonian is $\hat{H}=\frac{\hat{p}^2}{2m}+\frac{1}{2}m\omega^2\hat{x}^2$, and the commute relations is $[\hat{x},\hat{p}]=i\hbar$(Be careful of the sign!). Then the creation and annihilation operator can be defined as

@@

        And the commute relations is $[\hat{a}^\dagger, \hat{a}]=-1$(Be careful of the sign!). Inversely, $\hat{x}$, $\hat{p}$ and $\hat{H}$ can be described as

@@

        Therefore, we may define the coherent states as $\ket{\alpha} = \hat{D}(\alpha)\ket{0}$ with ANY complex number eigenvalue $\alpha\in\mathbb{C}$, and $\hat{a}\ket{\alpha}=\alpha\ket{\alpha}$.

        Since $\hat{a}^\dagger$ and $\hat{a}$ can be described by $\hat{x}$ and $\hat{p}$, we can write the translation operator as another form:

@@

@@

    \section{Coherent states under Hamiltonian and coordinate representation}

>>>>

    \section{Basic knowledges on oscillators}
        In this section, I'd like to briefly review some basic properties of some operators. The Hamiltonian is $\hat{H}=\frac{\hat{p}^2}{2m}+\frac{1}{2}m\omega^2\hat{x}^2$, and the commutation relation is $[\hat{x},\hat{p}]=i\hbar$(Be careful of the sign!). Then the creation and annihilation operator can be defined as

@@

        And the commutation relation is $[\hat{a}^\dagger, \hat{a}]=-1$(Be careful of the sign!). Inversely, $\hat{x}$, $\hat{p}$ and $\hat{H}$ can be described as

@@

        Therefore, we may define the coherent states as $\ket{\alpha} = \hat{D}(\alpha)\ket{0}$ with any complex number eigenvalue $\alpha\in\mathbb{C}$, and $\hat{a}\ket{\alpha}=\alpha\ket{\alpha}$. Note that all the translation opertors forms a group called Heisenberg-Weyl group. It's not difficult to find out that Heisenberg-Weyl group is isomorphic to $(\mathbb{C}, +)$, that is

        \begin{equation}        
            \hat{D}(\alpha)\hat{D}(\beta) = \hat{D}(\alpha+\beta)
        \end{equation}

        Since $\hat{D}(\alpha)$ is an operator on a linear space ,the Hilbert space for the oscillator, $\hat{D}(\alpha)$ can be regarded as a group representation of $(\mathbb{C}, +)$.

        Now that $\hat{a}^\dagger$ and $\hat{a}$ can be described by $\hat{x}$ and $\hat{p}$, we can write the translation operator as another form:

@@

        Recall that all $\hat{D}(\alpha)$ forms a group representation of $(\mathbb{C}, +)$, it can also be considered as a group representation of $(\mathbb{R}^2, +)$, where the $\mathbb{R}^2$ represnts the x and p coordinate, which is actually a point in the phase space. So a coherent state is actually a group action by a point in the phase space, and the evolution of a coherent state is a group action by a trajectory in the phase space.

@@

    \section{Hamiltonian representation and time evolution}

        It's not difficult to show that the expansion of a coherent state $\ket{\alpha}$ by the eigenstates of the Hamiltonian eigenstates is

        \begin{equation}
            \ket{\alpha} = e^{-|\alpha|^2/2} \sum \frac{\alpha^n}{\sqrt{n!}}\ket{n}
        \end{equation}

        Therefore the evolution of that state is $\ket{\alpha(t)}=e^{-i\hat{H}t/\hbar}\ket{\alpha}=\ket{\alpha} = e^{-|\alpha|^2/2} \sum \frac{\alpha^n}{\sqrt{n!}}e^{-iE_nt/\hbar}\ket{n}$. Since $E_n=(n+\frac{1}{2})\hbar\omega$, that factor can be written as $e^{-iE_nt/\hbar}=e^{-i\frac{1}{2}\omega t}e^{-in\omega t}=e^{-i\frac{1}{2}\omega t}\bigl(e^{-i\omega t}\bigr)^n$, where the latter phase can be combined with $\alpha^n$ and presents $(\alpha e^{-i\omega t})^n$ and $|\alpha e^{-i\omega t}|^2=|\alpha|^2$. Therefore,

        \begin{equation}
            \ket{\alpha(t)} = e^{-i\frac{1}{2}\omega t} \exp\bigl(-|\alpha e^{-i\omega t}|^2\bigr) \sum \frac{(\alpha e^{-i\omega})^n}{\sqrt{n!}}\ket{n}
        \end{equation}

        which suggests

        \begin{equation}
            \ket{\alpha(t)} = e^{-i\frac{1}{2}\omega t} \ket{\alpha e^{-i\omega t}}
        \end{equation}

    \section{Coherent states under coordinate representation}
